\chameleon{}: Untangling Type Errors Through Interactive Visualization and Exploration

### 2022-11-28 sections/evaluation.tex
Update images
Assets and code listing

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/participants-experience.png}
    \caption{}
    \label{fig:participant-experience}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/study-process.png}
    \caption{}
    \label{fig:study-process}
\end{figure}

@@

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/r1-data.pdf}
    \caption{Time to complete by task in user study 1 with confidence interval}
    \label{fig:r1-analysis}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/r2-data.pdf}
    \caption{Time to complete by task in user study 2 confidence interval}
    \label{fig:r2-analysis}
\end{figure}

@@

@@

The study of version 3 \chameleon{} is exploratory, in that we were hoping to let programmers discover their own way of using the tool. In post-hoc analysis of the collected log data, we were able to extrapolate some interesting patterns of how the tool was used. We share a few of our observations in this section.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/r4-analysis.pdf}
    \caption{Time to complete by task in user study 4 with confidence interval}
    \label{fig:r4-analysis}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/r4-task9.png}
    \caption{
High interaction users were able to locate the exact line for a potential fix after navigating to deduction step 6 or 7, which directly revealed the true cause of the type error. After this, 12 out of 15 high interaction users provided the most ideal fix in the first try. Low interaction group  takes longer time to examine the problem, provided wrong fixes in the initial trials. One participant fixed a minor run-time issue (a problematic pattern matching of `[attributes]` on line 18) however failed to identify the culprit of the type error.
    }
    \label{fig:r4-task9}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/r4-mode-switching.png}
    \caption{
        The rows represent the finishing mode, columns starting modes.
    }
    \label{fig:r4-mode-switching}
\end{figure}

>>>>

@@

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/procedure-1.pdf}
    \caption{}
    \label{fig:study-process}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/user-study-1a.pdf}
    \caption{Time to complete by task in user study 1a with confidence interval}
    \label{fig:r1-analysis}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/user-study-1b.pdf}
    \caption{Time to complete by task in user study 1b confidence interval}
    \label{fig:r2-analysis}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/procedure-2.pdf}
    \caption{}
    \label{fig:study-process}
\end{figure}

@@

The study of \chameleon{} 2 is exploratory, in that we were hoping to let programmers discover their own way of using the tool. In post-hoc analysis of the collected log data, we were able to extrapolate some interesting patterns of how the tool was used. We share a few of our observations in this section.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/user-study-2.pdf}
    \caption{Time to complete by task in user study 2 with 95\% confidence interval}
    \label{fig:r4-analysis}
\end{figure}

% \begin{figure}[h]
%     \centering
%     \includegraphics[width=\linewidth]{images/r4-task9.png}
%     \caption{
% High interaction users were able to locate the exact line for a potential fix after navigating to deduction step 6 or 7, which directly revealed the true cause of the type error. After this, 12 out of 15 high interaction users provided the most ideal fix in the first try. Low interaction group  takes longer time to examine the problem, provided wrong fixes in the initial trials. One participant fixed a minor run-time issue (a problematic pattern matching of `[attributes]` on line 18) however failed to identify the culprit of the type error.
%     }
%     \label{fig:r4-task9}
% \end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/mode-switching.pdf}
    \caption{
        The rows represent the finishing mode, columns starting modes.
    }
    \label{fig:r4-mode-switching}
\end{figure}

### 2022-11-28 sections/related-work.tex
Fix latex errors
Update images

\begin{figure}[h]
    \centering
    \Description{Chameleon interactive debugging and error message}
    \includegraphics[width=\linewidth]{images/original-chameleon.pdf}
    \caption{
Originally, Chameleon was a command-line tool that can list all the potential causes of a type error and display the two branches in two forms of highlight (right), achieved with ASCII colors. In addition, it allows a few commands (debug and explain) in the debugging shell to help debug type errors (left).}
    \label{fig:original-chameleon}
\end{figure}

>>>>

% \begin{figure}[h]
%     \centering
%     \includegraphics[width=\linewidth]{images/original-chameleon.pdf}
%     \caption{
% Originally, Chameleon was a command-line tool that can list all the potential causes of a type error and display the two branches in two forms of highlight (right), achieved with ASCII colors. In addition, it allows a few commands (debug and explain) in the debugging shell to help debug type errors (left).}
%     \label{fig:original-chameleon}
% \end{figure}
